---
title: "HAI CAI detection"
author: "Dung Vu Tien Viet"
date: "30 novembre 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
For the HAI/CAI detection, I use patient approach. That means I will evaluate each patient and decide that patient has CAI or HAI.

I use a knowledge database that I collected from VINARES data, point-prevalence survey in ICU (also in VINARES project) data, also from other papers over the world.

Each entry of this knowledge database will describe the probability of being in CAI if patients have one risk factor. 
For example, among all patients carrying Acinetobacter spp. (it is the risk factor), there are 30% of patients have CAI (and 70% has HAI).
So if I catch a patient with Acinetobacter spp., I will use a Bernoulli distribution with p=0.3 to generate a random value CAI/HAI for that patient.

Next, if patient's sample is blood. An another entry in the knowledge database indicate that $p_{CAI}(blood)=0.4$.
Now we have two indications (bacteria and specimen) to determine the CAI/HAI of that patient.

My question is: *how to combine two indications?*


We assume two factors A and B that correspond Acinetobacter spp. and blood; C is CAI. We have
$ P(C|A)=0.3;\ P(C|B)=0.4 $, that means probability of having CAI in patients carrying Acinetobacter is 0.3 and probability of having CAI in patients were taken blood = 0.4.

My question becomes the calculation of $P(C|(A\cap B))$.

$$
P(C|(A\cap B)) = \frac{P(C \cap (A \cap B))}{P(A \cap B)}
$$
$P(A \cap B) = P(A)*P(B)$ if A and B are independent. But it will be more difficult if A and B are dependent.

$P(C \cap (A \cap B))=P(C \cap A \cap B)$ is even no way to find out.

If I use Bayes' theorem,
$$
P(C|(A\cap B)) = \frac{P((A \cap B)|C)P(C)}{P(A \cap B)}
$$
I do not know either...

*Further, how to deal with three indications?*


I  stuck here. Do you have any idea or another approach?




```{r echo=FALSE}
#probability.CAI.HAI.factor <- 
#probability.CAI.HAI.bacteria.ab <-

# algorithm of HAI CAI
# Function decides infection source of patient
HAICAIdecision <- function(patient){
# patient: a vector containing all information of patient
  # Age, sex, hospial,ward, specimen type, bacteria
  
  
  
}

# sensitivity of algorithm


# end of function





```

