---
title: "HAI CAI prediction"
author: "Dung Vu Tien Viet"
date: "28 février 2019"
output:
  word_document: default
  html_document: default
---

```{r, echo=FALSE}
library(DataExplorer) 
library(dplyr) #mutate, arrange, 
library(caret) # predict
library(lubridate) #dmy
library(naivebayes) # naive_bayes
library(e1071) # svm
library(class) # knn
library(nnet) # multinom

library(ggplot2) #ggplot
library(knitr) #kable
library(purrr)
"%ni%" <- Negate("%in%")
###
```

This document describes the prediction process of source of infection (HAI/CAI).

The methods are in following steps:

(1) Import the baseline data from MALDITOF project
(2) Exploratory Data Analysis
(3)


```{r, echo=F}
# (1) baseline data importation
maldi <- read.csv("malditof.result.csv",stringsAsFactors = F)
maldi <- maldi[,c("Sex","Age","AdmissionDate","AdmissionTime","ward","Specimen","Specimen.Origin","InfectionReason","GDetectedDate","GDetectedTime","BacName")]
maldi$adm.growth <- (ymd(maldi$GDetectedDate) - ymd(maldi$AdmissionDate))*24+ 
  ifelse(is.na(maldi$GDetectedTime - maldi$AdmissionTime),0,(maldi$GDetectedTime - maldi$AdmissionTime) )
maldi$AgeCat <- cut(maldi$Age, breaks=c(-1,10, 20, 40, 60,100), right = TRUE)

maldi$BacGroup <- as.character(maldi$BacName)
maldi$BacGroup[maldi$BacName %ni% 
                                 c("Escherichia coli","Streptococcus suis","Cryptococcus neoformans",
                                   "Staphylococcus aureus","Klebsiella pneumoniae","Streptococcus suis type 2",
                                   "Penicillium marneffei","Streptococcus pneumoniae","Salmonella sp.","Pseudomonas pseudomallei",
                                   "Pseudomonas aeruginosa","Acinetobacter baumannii","Pseudomonas pseudomallei")] <- "Others"
maldi$BacGroup[maldi$BacGroup=="Streptococcus suis type 2"] <- "Streptococcus suis" # correct S.suis name

maldi$Specimen <- ifelse(maldi$Specimen.Origin %ni% c("BLOOD","CSF"),"Other",maldi$Specimen.Origin)
maldi$HAICAI <- ifelse(maldi$adm.growth>48,"HAI","CAI")

maldi[,c("Sex","AgeCat","ward","Specimen","BacGroup")] <- apply(maldi[,c("Sex","AgeCat","ward","Specimen","BacGroup")],2,as.factor)
```

VINARES importation

```{r, echo=FALSE}
VNRresult <- read.csv("vinares.result.csv",stringsAsFactors = F)
VNRresult$AGE_GROUP[VNRresult$AGE_GROUP==""] <- NA
VNRresult$Sex <- ifelse(VNRresult$SEX=="f","FEMALE",ifelse(VNRresult$SEX=="m","MALE",NA))
VNRresult$AgeCat <- plyr::mapvalues(VNRresult$AGE_GROUP,
                                         from = levels(factor(VNRresult$AGE_GROUP)),to = sort(unique(maldi$AgeCat)))
VNRresult$ward <- ifelse(VNRresult$DEPARTMENT %in% 
                                c("C?p C?", "cc", "CC", "ccdk", "cchs", "cctm","HS","hscc", "HSCC", "hsn","HSN", "hsng", "icu", "NICU"), "Critical Care","Other")

VNRresult$Specimen <- ifelse(VNRresult$SPEC =='bl',"BLOOD",
                                  ifelse(VNRresult$SPEC =='sf',"CSF","Other"))

VNRresult$BacGroup <- plyr::mapvalues(VNRresult$Bacgroup,
                                         from = as.character(sort(unique(VNRresult$Bacgroup))),
                                         to = c("Acinetobacter baumannii","Escherichia coli",
                                                "Others","Others","Others","Klebsiella pneumoniae",
                                                "Others","Pseudomonas aeruginosa","Staphylococcus aureus",
                                                "Streptococcus pneumoniae"))



#VNRresult[,c("Sex","AgeCat","ward","Specimen","BacGroup")] <- as.data.frame(lapply(c("Sex","AgeCat","ward","Specimen","BacGroup"),function(x){VNRresult[,x] <- factor(VNRresult[,x],levels = levels(input.data[,x]))}))

```

```{r, echo=F}
#(2) Explainatory Data Analysis

# predict VINARES dataset: use blood and CSF only
input.data <- maldi[maldi$Specimen %in% c("BLOOD","CSF"),c("Sex","Age","AgeCat","ward","Specimen","BacName","BacGroup","AdmissionDate","adm.growth","HAICAI")]
plot_str(input.data)
plot_missing(input.data)
plot_bar(input.data)
# correlation btw variables
chisq.test(input.data$Specimen,input.data$BacGroup)
chisq.test(input.data$ward,input.data$BacGroup)
chisq.test(input.data$Specimen,input.data$ward)
create_report(input.data)
```

```{r, echo=F}
# (3) generate models from predictors
generate_formula <- function(input_vector){
  # input_vector: a vector of all variable names
  l <- list()
  for (i in 1:length(input_vector)){
    l[[i]] <-c(TRUE,FALSE) 
  }

  l %>% expand.grid() %>% apply(1,function(x){paste("HAICAI ~ ",paste(input_vector[unlist(x)],collapse = " + "))})->all.models
  
  all.models[1:(2^length(input_vector)-1)]
  
}
```


Write a function that estimates accuracy of all models and predict the HAICAI. 

Input: training data, data need to predict HAICAI, vector of predictor variables and classification methods will be used

Output: a list of (1) accuracy of models and (2) HAICAI prediction of all models

```{r, echo=FALSE}

pred.multiple.models <- function(training,data.to.predict,predictors,classification.methods){
  # (1) all combinations of formulas and methods
  all.formulas.methods <- expand.grid(generate_formula(predictors),classification.methods)
  # (2) estimate accuracy of models
    set.seed(1)
  train_control <- trainControl(method="repeatedcv", number = 2, repeats=2)
  
  call.train <- function(formula,method){
  train(as.formula(as.character(formula)),data=training,method = method, trControl=train_control)}
  
  map2(all.formulas.methods$Var1,all.formulas.methods$Var2,call.train) -> all.models
  all.models %>% lapply(function(x){max(x$results$Accuracy)}) %>% as.data.frame %>% t -> accuracy
  all.formulas.methods %>% mutate(max.accuracy = accuracy) -> all.formulas.methods
  #(3) predict and return results
  list(accuracy=all.formulas.methods,pred=predict(all.models,data.to.predict))
}

x <- pred.multiple.models(training = maldi[maldi$Specimen %in% c("BLOOD","CSF"),c("Specimen","ward","BacGroup","HAICAI")],data.to.predict = VNRresult[VNRresult$Specimen %in% c("BLOOD","CSF"),c("Specimen","ward","BacGroup")],predictors = c("ward","BacGroup"),classification.methods = c("multinom","adaboost"))

```


Compare data distribution between MALDITOF and VINARES

```{r,echo=F}
prop.table(table(maldi[,c("Specimen","BacGroup")])) %>% as.data.frame %>% arrange(Freq) %>%
  (function(x){ggplot(data = x,aes(Specimen,BacGroup,fill=Freq))+geom_tile()+ scale_fill_gradient(low = "white", high = "red")})

prop.table(table(VNRresult[,c("Specimen","BacGroup")])) %>% as.data.frame %>% arrange(Freq) %>%
  (function(x){ggplot(data = x,aes(Specimen,BacGroup,fill=Freq))+geom_tile()+ scale_fill_gradient(low = "white", high = "red")})

```

Compare HAI/CAI distribution between MALDITOF and VINARES

```{r,echo=F}

kable(cbind(as.data.frame(table(maldi[maldi$HAICAI=="HAI",c("Specimen","BacGroup")])),
                    as.data.frame(table(maldi[,c("Specimen","BacGroup")]))))

kable(table(maldi[maldi$HAICAI=="HAI",c("Specimen","BacGroup")])/table(maldi[,c("Specimen","BacGroup")]))

as.data.frame(table(maldi[maldi$HAICAI=="HAI",c("Specimen","BacGroup")])/table(maldi[,c("Specimen","BacGroup")])) %>% arrange(Freq) %>%
  (function(x){ggplot(data = x,aes(Specimen,BacGroup,fill=Freq))+geom_tile()+ scale_fill_gradient(low = "white", high = "red")})


### VINARES

kable(cbind(as.data.frame(table(VNRresult[VNRresult$HAICAI=="HAI",c("Specimen","BacGroup")])),
                    as.data.frame(table(VNRresult[,c("Specimen","BacGroup")]))))


kable(table(VNRresult[VNRresult$HAICAI=="HAI",c("Specimen","BacGroup")])/table(VNRresult[,c("Specimen","BacGroup")]))

as.data.frame(table(VNRresult[VNRresult$HAICAI=="HAI",c("Specimen","BacGroup")])/table(VNRresult[,c("Specimen","BacGroup")])) %>% arrange(Freq) %>%
  (function(x){ggplot(data = x,aes(Specimen,BacGroup,fill=Freq))+geom_tile()+ scale_fill_gradient(low = "white", high = "red")})


```
